### 2018-02-24 DASFAA18_CR/Gruba_final/06-perf.tex

\stitle{Exp-1: Feature Extraction}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
System \sys{} reaches the optimal results when $\alpha$ is 0.7,
upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
In general, it performs well when $\alpha$ falls into $[0, 0.8]$.

@@

\begin{figure*}[tb!]
  \centering
  \subfigure[Tests with Various $\alpha$.]{
    \label{fig:fe}
\includegraphics[width=.355\linewidth]{figures/Interests}}
  \hspace{0.5in}
   \subfigure[Silhouette Coefficient Tests.]{
    \label{fig:10-c}
  \includegraphics[width=.355\linewidth]{figures/clustering}}
%  \caption{Performance of \sys{} Versus LRC-BQ.}
    \label{fig:fig-1}
    \vspace{-4ex}
\end{figure*}

@@

\begin{figure*}[tb!]
\centering
  \subfigure[Accuracy of \sys{} Versus LRC-BQ.]{
    \label{fig:10-a}
    \includegraphics[width=0.355\textwidth]{figures/precision-1.eps}}
  \hspace{0.5in}
   \subfigure[Accuracy of Using Various Data Items for Modeling of \sys{}.]{
    \label{fig:11-a}
  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures.eps}}
  \caption{Performance of \sys{} }
  \label{fig:fig-2}
  \vspace{-4ex}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
  \vspace{-4ex}
\end{figure*}

@@

\textbf{Summary}. From these experimental results we find the followings.
(1) We design a novel method to extract users' explicit/implicit interests. And we tested various $\alpha$ to get a good performance. The visualization for a typical user shows that our method can make sense.
(2) In this paper, we offer a clustering method K-Gru to deal with complex vectors. And it helps us find a reasonable clustering result.
(3) By modeling user behaviors over groups instead of a single model for all users as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%. What deserves to be mentioned is that the performance of LRC-BQ also improved a lot by user clustering.

>>>>

\stitle{Exp-1: Feature Extraction}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values.
We report the interest accuracy with various $\alpha$ values. Suppose the label set manually labeled for each microblog is $A$, the label set our method labeled is $B$.
The interest accuracy is defined as $\frac{ A \cap B }{ A \cup B }$.

System \sys{} reaches the optimal results when $\alpha$ is 0.7,
upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million microblogs.
In general, it performs well when $\alpha$ falls into $[0, 0.8]$.

@@

@@

\begin{figure*}[tb!]
  \centering
  \subfigure[Tests with Various $\alpha$.]{
    \label{fig:fe}
\includegraphics[width=.355\linewidth]{figures/Interests}}
  \hspace{0.5in}
   \subfigure[Silhouette Coefficient Tests.]{
    \label{fig:10-c}
  \includegraphics[width=.355\linewidth]{figures/clustering}}
%  \caption{Performance of \sys{} Versus LRC-BQ.}
    \label{fig:fig-1}

  \subfigure[Accuracy of \sys{} Versus LRC-BQ.]{
    \label{fig:10-a}
    \includegraphics[width=0.355\textwidth]{figures/precision-1.eps}}
  \hspace{0.5in}
   \subfigure[Accuracy of Using Various Data Items for Modeling of \sys{}.]{
    \label{fig:11-a}
  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures.eps}}
  \caption{Performance of \sys{} }
  \label{fig:fig-2}
  \vspace{-4ex}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[]{
      \label{fig:userFeatures:uf-1}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/1.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-2}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/2.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-3}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/3.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-4}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/4.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-5}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/5.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-6}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/6.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-7}
      \includegraphics[width=0.23\textwidth]{IMAGE/features/userFeatures/7.eps}}
  \subfigure[]{
      \label{fig:userFeatures:uf-8}
      \includegraphics[width=0.24\textwidth]{IMAGE/features/userFeatures/8.eps}}
  \caption{Visualization for User Features.}
  \label{fig:userFeatures} %% label for entire figure
  \vspace{-2ex}
\end{figure*}

@@

To conclude, by modeling user behaviors over groups instead of a single model for all users such as LRC-BQ, we improve the average accuracy over LRC-BQ by 6\%. What deserves to be mentioned is that the performance of LRC-BQ is also improved significantly by user clustering.
